\bf Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-03-23 doc/paper.Rmd
couple of wrong assumptions uncovered

\tableofcontents
\newpage
```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  error = FALSE, 
  collapse = TRUE,
  comment = "",
  fig.height = 6,
  fig.width = 6,
  fig.align = "center",
  out.width= '\\textwidth',
  cache = FALSE,
  fig.path='figures/',
  echo=FALSE,
  cache=TRUE
)
options(knitr.table.format = "latex")
library(tidyverse)
library(kableExtra)
```

@@

all$coarse <- 1
errors <- rbind(errorrate(all, 0.001), 
                errorrate(all, 0.005), 
                errorrate(all, 0.01), 
                errorrate(all, 0.05))

@@

errors2 <- rbind(errorrate(allp, 0.001), 
                errorrate(allp, 0.005), 
                errorrate(allp, 0.01), 
                errorrate(allp, 0.05))

@@

Figure \ref{fig:prof_missings} (a) shows the type II error rates for profiles for the optimization window 120 and validation window 30 with varying level of coarseness. We can see that the type II error for all the nominal $\alpha$ levels is lowest in the range of 0.20 to 0.35. Therefore, a value of 0.25 can be used keeping in mind it keeps the type II error lowest while runnning simulations. Thus for comparisons of different window sizes etc as seen in the differnt parts of Figure \ref{fig:prof_missings} this coarseness value is used.

### Comparison of profiles and signatures

#multiplot(plotlist = list(total1, total2, miss_1, miss_2, e1, e2), cols = 2)#, matrix(c(1,2,3,3), nrow=2, byrow=TRUE))
multiplot(plotlist = list(e1, total1, total2,e2, miss_1, miss_2), cols = 2)
```
 \pagebreak

## Conclusion

@@

>>>>

\tableofcontents
\newpage
```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  error = FALSE, 
  collapse = TRUE,
  comment = "",
  fig.height = 6,
  fig.width = 6,
  fig.align = "center",
  out.width= '\\textwidth',
  cache = FALSE,
  fig.path='figures/',
  echo=FALSE,
  cache=TRUE
)
options(knitr.table.format = "latex")
library(tidyverse)
library(kableExtra)
library(xtable)
```

@@

all$coarse <- 1
errors <- rbind(errorrate(all, 0.001), 
                errorrate(all, 0.005), 
                errorrate(all, 0.01), 
                errorrate(all, 0.05))
errors$type <- "signatures"

@@

errors2 <- rbind(errorrate(allp, 0.001), 
                errorrate(allp, 0.005), 
                errorrate(allp, 0.01), 
                errorrate(allp, 0.05))
errors2$type <- "profiles"

@@

\hh{When dealing with profiles, coarseness is an additional parameter that has to be considered in the matching.}

\hh{XXX We have been operating under a false assumption: smoothing the signature at f=1 DOES change it - see figure \ref{fig:profile-sketch}. We need to re-run some of the results to compare the results against a }

```{r profile-sketch, fig.height = 3, fig.width='\\textwidth'}
profile <- sigs_graphics[[1]] %>% filter(land_id==19)
profile$lw25 <- lowess(x = profile$y, y = profile$value, f=.25)$y
profile$lw50 <- lowess(x = profile$y, y = profile$value, f=.5)$y
profile$lw75 <- lowess(x = profile$y, y = profile$value, f=.75)$y
profile$lw100 <- lowess(x = profile$y, y = profile$value, f=1)$y

profile$l25 <- predict(loess(data = profile, value~y, span=.25))
profile$l50 <- predict(loess(data = profile, value~y, span=.5))
profile$l75 <- predict(loess(data = profile, value~y, span=.75))
profile$l100 <- predict(loess(data = profile, value~y, span=2))

pw1 <- profile %>%
  ggplot(aes(x = y, y = value-lw25)) + geom_line() +
  theme_bw() +
  ylab(expression(paste("Depth (in ",mu,m,")", sep=""))) + 
  xlab(expression(paste("Relative Location (in ",mu,m,")", sep=""))) + 
  ggtitle("Coarseness 0.25")

pw2 <- profile %>%
  ggplot(aes(x = y, y = value-lw50)) + geom_line() +
  theme_bw() +
  ylab(expression(paste("Depth (in ",mu,m,")", sep=""))) + 
  xlab(expression(paste("Relative Location (in ",mu,m,")", sep=""))) + 
  ggtitle("Coarseness 0.5")

pw3 <- profile %>%
  ggplot(aes(x = y, y = value-lw75)) + geom_line() +
  theme_bw() +
  ylab(expression(paste("Depth (in ",mu,m,")", sep=""))) + 
  xlab(expression(paste("Relative Location (in ",mu,m,")", sep=""))) + 
  ggtitle("Coarseness 0.75")

pw4 <- profile %>%
  ggplot(aes(x = y, y = value-lw100)) + geom_line() +
  theme_bw() +
  ylab(expression(paste("Depth (in ",mu,m,")", sep=""))) + 
  xlab(expression(paste("Relative Location (in ",mu,m,")", sep=""))) + 
  ggtitle("Coarseness 1")

p1 <- profile %>%
  ggplot(aes(x = y, y = value-l25)) + geom_line() +
  theme_bw() +
  ylab(expression(paste("Depth (in ",mu,m,")", sep=""))) + 
  xlab(expression(paste("Relative Location (in ",mu,m,")", sep=""))) + 
  ggtitle("Coarseness 0.25")

p2 <- profile %>%
  ggplot(aes(x = y, y = value-l50)) + geom_line() +
  theme_bw() +
  ylab(expression(paste("Depth (in ",mu,m,")", sep=""))) + 
  xlab(expression(paste("Relative Location (in ",mu,m,")", sep=""))) + 
  ggtitle("Coarseness 0.5")

p3 <- profile %>%
  ggplot(aes(x = y, y = value-l75)) + geom_line() +
  theme_bw() +
  ylab(expression(paste("Depth (in ",mu,m,")", sep=""))) + 
  xlab(expression(paste("Relative Location (in ",mu,m,")", sep=""))) + 
  ggtitle("Coarseness 0.75")

p4 <- profile %>%
  ggplot(aes(x = y, y = value-l100)) + geom_line() +
  theme_bw() +
  ylab(expression(paste("Depth (in ",mu,m,")", sep=""))) + 
  xlab(expression(paste("Relative Location (in ",mu,m,")", sep=""))) + 
  ggtitle("Coarseness 1")

prof  <- profile %>% ggplot(aes (x = y, y = value)) + geom_line() +
  theme_bw() +
  ylab(expression(paste("Depth (in ",mu,m,")", sep=""))) + 
  xlab(expression(paste("Relative Location (in ",mu,m,")", sep=""))) + 
  ggtitle("Profile")
grid.arrange(pw1, pw2, pw3, pw4, p1, p2, p3, p4, prof, ncol=4)
```

\hh{Figure \ref{fig:coarse} shows the type II error rates for profiles using an optimization window $w_o= 120$ and a validation window $w_v = 30$ for varying level of coarseness. The type II error for all nominal levels of  $\alpha$ are the lowest for a coarseness range of 0.20 to 0.35. For the remainder of the analysis we use a fixed value of coarseness of 0.25. }

```{r coarse, fig.cap="Type II error with respect to coarseness parameter over profiles, $w_o = 120$, $w_v = 30$. Optimal values for coarseness are around $c \\approx 0.30$", fig.width=5, fig.height = 3, out.width='.6\\textwidth'}
e1<-errors2 %>% filter(wv==30)%>% ggplot(aes(x = coarse, y=beta, colour=factor(alpha))) +
  geom_point() + geom_line() +
  theme_bw() +
  scale_colour_brewer(expression("Nominal\ntype I error"~alpha), palette="Set2") + xlab("Profile Coarseness")+
  ylab("Type II error") 
e1
```

```{r, include =F}
wo120_sig <- errors %>% filter(wo==120, wv %in% c(30, 50))
wo120_pr <- errors2 %>% filter(wo==120, wv %in% c(30, 50), coarse == .25)

dt <- rbind(wo120_sig, wo120_pr) %>% 
  ungroup() %>% 
  mutate(beta = round(100*beta, 1)) %>%
  select(wv, type, alpha, beta) %>% 
  spread(alpha, beta)
print(xtable(dt), include.rownames=FALSE)
```

\begin{table}[ht]
\caption{\label{tab:type2} Type II error rates for profiles and signatures of bullet lands. For profiles, a coarseness value of $c = 0.25$ is used to remove bullet curvature.}
\centering
\begin{tabular}{rlrrrr}
  \hline
optimization && \multicolumn{4}{l}{Nominal type I error rate $\alpha$}\\  
window $w_o$ & source & 0.001 & 0.005 & 0.01 & 0.05 \\ 
  \hline
 30 & profiles & 54.40 & 43.80 & 39.70 & 30.00 \\ 
   30 & signatures & 55.00 & 45.40 & 41.40 & 31.10 \\ \hline
   50 & profiles & 58.50 & 44.40 & 40.70 & 28.70 \\ 
   50 & signatures & 62.60 & 49.60 & 44.20 & 30.50 \\ 
   \hline
\end{tabular}
\end{table}

# Conclusion

@@

# Appendix
\begin{appendix}

\subsection{Comparison of profiles and signatures}

#multiplot(plotlist = list(total1, total2, miss_1, miss_2, e1, e2), cols = 2)#, matrix(c(1,2,3,3), nrow=2, byrow=TRUE))
multiplot(plotlist = list(e1, total1, total2,e2, miss_1, miss_2), cols = 2)
```
\end{appendix}

### 2018-03-23 doc/paper.tex
couple of wrong assumptions uncovered

Figure \ref{fig:prof_missings} (a) shows the type II error rates for
profiles for the optimization window 120 and validation window 30 with
varying level of coarseness. We can see that the type II error for all
the nominal \(\alpha\) levels is lowest in the range of 0.20 to 0.35.
Therefore, a value of 0.25 can be used keeping in mind it keeps the type
II error lowest while runnning simulations. Thus for comparisons of
different window sizes etc as seen in the differnt parts of Figure
\ref{fig:prof_missings} this coarseness value is used.

On the other hand Figure \ref{fig:prof_missings} (b) shows if the
coarseness level set in the chumbley agorithm has any effect on the
signatures, which are pre-processed and already smoothed to a certain
extent. From Figure \ref{fig:prof_missings} (b) we can notice that for
different nominal \(\alpha\) levels, the type II error fluctuates
slightly but does not change much, thereby helping us conclude that the
coarseness levels set in the LOWESS smoothing in the chumbley alggorithm
does effect the type II error much for signatures.

\subsubsection{Comparison of profiles and
signatures}\label{comparison-of-profiles-and-signatures}

@@

\caption{Row 3:  Total error and Number of failed tests by the window validation size, wv, and ground truth, Row 2: Total error and Number of failed tests with Coarseness for both profiles and signatures, Row 1: Type II error for different coarseness levels as used in the modified chumbley algorithm for profiles and signatures}\label{fig:prof_missings}
\end{figure}

\pagebreak

\subsection{Conclusion}\label{conclusion}

>>>>

\hh{When dealing with profiles, coarseness is an additional parameter that has to be considered in the matching.}

\hh{XXX We have been operating under a false assumption: smoothing the signature at f=1 DOES change it - see figure \ref{fig:profile-sketch}. We need to re-run some of the results to compare the results against a }

\begin{center}\includegraphics[width=\textwidth]{figures/profile-sketch-1} \end{center}

\hh{Figure \ref{fig:coarse} shows the type II error rates for profiles using an optimization window $w_o= 120$ and a validation window $w_v = 30$ for varying level of coarseness. The type II error for all nominal levels of  $\alpha$ are the lowest for a coarseness range of 0.20 to 0.35. For the remainder of the analysis we use a fixed value of coarseness of 0.25. }

{\centering \includegraphics[width=.6\textwidth]{figures/coarse-1}

\caption{Type II error with respect to coarseness parameter over profiles, $w_o = 120$, $w_v = 30$. Optimal values for coarseness are around $c \approx 0.30$}\label{fig:coarse}
\end{figure}

\begin{table}[ht]
\caption{\label{tab:type2} Type II error rates for profiles and signatures of bullet lands. For profiles, a coarseness value of $c = 0.25$ is used to remove bullet curvature.}
\centering
\begin{tabular}{rlrrrr}
  \hline
optimization && \multicolumn{4}{l}{Nominal type I error rate $\alpha$}\\  
window $w_o$ & source & 0.001 & 0.005 & 0.01 & 0.05 \\ 
  \hline
 30 & profiles & 54.40 & 43.80 & 39.70 & 30.00 \\ 
   30 & signatures & 55.00 & 45.40 & 41.40 & 31.10 \\ \hline
   50 & profiles & 58.50 & 44.40 & 40.70 & 28.70 \\ 
   50 & signatures & 62.60 & 49.60 & 44.20 & 30.50 \\ 
   \hline
\end{tabular}
\end{table}

\section{Conclusion}\label{conclusion}

\section{Appendix}\label{appendix}

\begin{appendix}

On the other hand Figure \ref{fig:prof_missings} (b) shows if the coarseness level set in the chumbley agorithm has any effect on the signatures, which are pre-processed and already smoothed to a certain extent. From Figure \ref{fig:prof_missings} (b) we can notice that for different nominal $\alpha$ levels, the type II error fluctuates slightly but does not change much, thereby helping us conclude that the coarseness levels set in the LOWESS smoothing in the chumbley alggorithm does effect the type II error much for signatures.

\subsection{Comparison of profiles and signatures}

@@

\caption{Row 3:  Total error and Number of failed tests by the window validation size, wv, and ground truth, Row 2: Total error and Number of failed tests with Coarseness for both profiles and signatures, Row 1: Type II error for different coarseness levels as used in the modified chumbley algorithm for profiles and signatures}\label{fig:prof_missings}
\end{figure}
\end{appendix}
